Anomalous waves triggered by abrupt depth changes: experimental measurements and deterministic-statistical truncated KdV theory

### 2019-10-07 paper2_JNLS/paper.tex
NM

All parameters that appear in the theoretical model follow directly from experimental parameters, with the exception of the inverse temperature, $\thup$, of the incoming flow and the parameter $\lamfac$, which represents the number of characteristic wavelengths in the periodic domain. The parameter $\lamfac$ can be chosen in a sensible way by simply selecting an intermediate value between 1 and $\Lambda$, so that some scales both larger than and smaller than the characteristic wavelength $\lam$ are resolved. Hence, we will simply chose $\lamfac = \Lambda/2$ throughout, so that on a log-scale, the characteristic wavelength lies directly in the middle of the resolved wavelengths. The incoming inverse temperature, $\thup$, however, is more difficult to pin down without using information from the experiments. Our strategy is to use the outgoing skewness as the main diagnostic to determine a realistic range for $\thup$. That is, for an input $\thup$, the downstream inverse temperature $\thdn$ is determined by \eqref{statmatch}, which ultimately sets the skewness of the outgoing wave-field.

@@

Figure \ref{transfig}(a) shows the transfer function $\thdn = \transf(\thup)$ that results from the statistical matching condition \eqref{statmatch}, for an incoming inverse temperature in the range $\thup \in [0,20]$. In this figure, all model parameters are set by their experimental values, and we show the cases $\Lambda = 8, 16, 32$ with $\lamfac = \Lambda/2$ in each. As seen here, the transfer function is relatively insensitive to the truncation index since all three curves are relatively close to one another. This insensitivity is a consequence of scaling $\lamfac$ with $\Lambda$ appropriately as discussed previously.

>>>>

All parameters that appear in the theoretical model follow directly from experimental parameters, with the exception of the inverse temperature of the incoming flow, $\thup$, and the parameter $\lamfac$, which represents the number of characteristic wavelengths in the periodic domain. The parameter $\lamfac$ can be chosen in a sensible way by simply selecting an intermediate value between 1 and $\Lambda$, so that some scales both larger than and smaller than the characteristic wavelength $\lam$ are resolved. Hence, we will simply chose $\lamfac = \Lambda/2$ throughout, so that on a log-scale, the characteristic wavelength lies directly in the middle of the resolved wavelengths. The incoming inverse temperature, $\thup$, however, is more difficult to pin down without using information from the experiments. Our strategy is to use the outgoing skewness as the main diagnostic to determine a realistic range for $\thup$. That is, for an input $\thup$, the downstream inverse temperature $\thdn$ is determined by \eqref{statmatch}, which ultimately sets the skewness of the outgoing wave-field.

@@

Figure \ref{transfig}(a) shows the transfer function $\thdn = \transf(\thup)$ that results from the statistical matching condition \eqref{statmatch}, for an incoming inverse temperature in the range $\thup \in [0,20]$. In this figure, all model parameters are set by their experimental values, and we show the cases $\Lambda = 8, 16, 32$ with $\lamfac = \Lambda/2$ in each. As seen here, the transfer function is relatively insensitive to the truncation index since all three curves are relatively close to one another. This insensitivity is a consequence of scaling $\lamfac$ with $\Lambda$ appropriately as discussed previously. \nick{(I should show the little calculation that justifies this)}

\nick{PICK IT UP AROUND HERE}
